Structured Versus Decorated Cospans

### 2021-06-23 cospans_new.tex
Fixed stuff at end of Section 4 - check it out!

Moreover, each fiber $\X_a=F(a)$ obtains a monoidal structure via 
\begin{equation}\label{eq:explicitstructure1}
\otimes_a\maps F(a)\times F(a)\xrightarrow{\phi_{a,a}}F(a+a)\xrightarrow{F(\nabla)}F(a),\quad
I_a\maps\one\xrightarrow{\phi_0}F(0)\xrightarrow{F(!_a)}F(a)
\end{equation}
where $\nabla$ is the fold map, which is symmetric when $F$ is, again via the components of $u_{a,a}$. Also, each reindexing functor $f_!=F(f)$ obtains a strong monoidal structure with
\begin{equation}\label{eq:strongreindexing}
\begin{tikzcd}[row sep=.35in]
 F(a)\times F(a)\ar[r,"\phi_{a,a}"]\ar[d,"F(f)\times F(f)"']\ar[dr,phantom,"{\stackrel[\cref{eq:pseudonaturality}]{\phi_{f,f}}{\cong}}"] & 
 F(a+a)\ar[r,"F(\nabla)"]\ar[d,"F(f+f)"description]\ar[dr,phantom,"\cong"] & F(a)\ar[d,"F(f)"] \\
 F(b)\times F(b)\ar[r,"\phi_{b,b}"'] & F(b+b)\ar[r,"F(\nabla)"'] & F(b)
\end{tikzcd}
\end{equation}
\end{proof}

@@

Given the hypothesis of \cref{thm:equiv}, the isomorphism from $F\lCsp$ to ${}_L\lCsp(\inta F)$ works as follows.   It is the identity on objects and vertical morphisms, 
which are just objects and morphisms of $\A$.   It maps the decorated cospan
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,0) {$m$};
\node (C) at (2,0) {$b$,};
\node (D) at (3,0) {$s \in F(m)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B);
\end{tikzpicture}
\]
to the structured cospan
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(a)$};
\node (B) at (1.5,0) {$(m,s)$};
\node (C) at (3,0) {$L(a)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$\utilde{i}$} (B)
(C) edge node[above]{$\utilde{o}$} (B);
\end{tikzpicture}
\]
where $L(a)$ is the initial object in the fiber of $\X = \inta F$ over $a \in A$, namely $(a,I_a)$ 
where $I_a \in F(a)$ is the \define{trivial decoration} given in \cref{eq:explicitstructure1}, and
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$\one$};
\node (B) at (1,0) {$F(0)$};
\node (C) at (2.2,0.5) {$F(a)$};
\node (C') at (2.2,-0.5) {$F(b)$};
\node (D) at (1.8,0) {$\cong$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$\phi_0$} (B)
(B) edge node[above]{$F(!_a)\;$} (C)
(B) edge node[below]{$F(!_b)\;\;$} (C')
(C) edge node[right]{$F(f)$} (C');
\end{tikzpicture}
\]
{\john NOT DONE!!!}

   Finally, this isomorphism maps the map of decorated cospans
\[
\begin{tikzpicture}[scale=1.5,baseline=(current bounding box.center)]
\node (A) at (0,0.5) {$a$};
\node (A') at (0,-0.5) {$a'$};
\node (B) at (1,0.5) {$m$};
\node (C) at (2,0.5) {$b$};
\node (C') at (2,-0.5) {$b'$};
\node (D) at (1,-0.5) {$m'$};
\node (E) at (3,0.5) {$s \in F(m)$};
\node (F) at (3,-0.5) {$s' \in F(m')$};
\node (G) at (1,-1) {$\tau \maps F(h)(s) \to s'$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B)
(A) edge node[left]{$f$} (A')
(C) edge node[right]{$g$} (C')
(A') edge node[below] {$i'$} (D)
(C') edge node[below] {$o'$} (D)
(B) edge node [left] {$h$} (D);
\end{tikzpicture}
\]
to this map of structured cospans:
\[
\begin{tikzpicture}[scale=1.5,baseline=(current bounding box.center)]
\node (A) at (0,0.5) {$L(a)$};
\node (A') at (0,-0.5) {$L(a')$};
\node (B) at (1,0.5) {$(m,s)$};
\node (C) at (2,0.5) {$L(b)$};
\node (C') at (2,-0.5) {$b'$.};
\node (D) at (1,-0.5) {$(m',s')$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$\utilde{i}$} (B)
(C) edge node[above]{$\utilde{o}$} (B)
(A) edge node[left]{$L(f)$} (A')
(C) edge node[right]{$L(g)$} (C')
(A') edge node[below] {$\utilde{i}'$} (D)
(C') edge node[below] {$\utilde{o}'$} (D)
(B) edge node [left] {$(h,\tau)$} (D);
\end{tikzpicture}
\]

@@

\node (L) at (1,-1.5) {$\tau_{b} = 1_{I_b}$};

>>>>

Moreover, each fiber $\X_a=F(a)$ obtains a monoidal structure via 
\begin{equation} \label{eq:explicitstructure1}
\otimes_a\maps F(a)\times F(a)\xrightarrow{\phi_{a,a}}F(a+a)\xrightarrow{F(\nabla)}F(a),\quad
I_a\maps\one\xrightarrow{\phi_0}F(0)\xrightarrow{F(!_a)}F(a)
\end{equation}
where $\nabla$ is the fold map, which is symmetric when $F$ is, again via the components of $u_{a,a}$. Also, each reindexing functor $f_!=F(f)$ obtains a strong monoidal structure with
\begin{equation}\label{eq:strongreindexing}
\begin{tikzcd}[row sep=.35in]
 F(a)\times F(a)\ar[r,"\phi_{a,a}"]\ar[d,"F(f)\times F(f)"']\ar[dr,phantom,"{\stackrel[\cref{eq:pseudonaturality}]{\phi_{f,f}}{\cong}}"] & 
 F(a+a)\ar[r,"F(\nabla)"]\ar[d,"F(f+f)"description]\ar[dr,phantom,"\cong"] & F(a)\ar[d,"F(f)"] \\
 F(b)\times F(b)\ar[r,"\phi_{b,b}"'] & F(b+b)\ar[r,"F(\nabla)"'] & F(b)
\end{tikzcd}
\end{equation}
\end{proof}

@@

Given the hypothesis of \cref{thm:equiv}, the isomorphism from $F\lCsp$ to ${}_L\lCsp(\inta F)$ works as follows.   It is the identity on objects and vertical morphisms, 
which are just objects and morphisms of $\A$.   It maps the decorated cospan
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,0) {$m$};
\node (C) at (2,0) {$b$,};
\node (D) at (3,0) {$s \in F(m)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B);
\end{tikzpicture}
\]
to the structured cospan
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$(a,I_a)$};
\node (B) at (1.5,0) {$(m,s)$};
\node (C) at (3,0) {$(b,I_b)$.};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$(i,!)$} (B)
(C) edge node[above]{$(o,!)$} (B);
\end{tikzpicture}
\]
Here $I_a \in F(a)$ is the \define{trivial decoration} given by the composite
\[  \one\xrightarrow{\phi_0}F(0)\xrightarrow{F(!_a)}F(a), \]
while $! \maps F(i)(I_a) \to s$ is the unique morphism with this domain and
codomain (recall that $F(i)$ preserves initial objects), and similarly for
$! \maps F(o)(I_b) \to s$.   Finally, this isomorphism sends the map of decorated cospans
\[
\begin{tikzpicture}[scale=1.5,baseline=(current bounding box.center)]
\node (A) at (0,0.5) {$a$};
\node (A') at (0,-0.5) {$a'$};
\node (B) at (1,0.5) {$m$};
\node (C) at (2,0.5) {$b$};
\node (C') at (2,-0.5) {$b'$};
\node (D) at (1,-0.5) {$m'$};
\node (E) at (3,0.5) {$s \in F(m)$};
\node (F) at (3,-0.5) {$s' \in F(m')$};
\node (G) at (1,-1) {$\tau \maps F(h)(s) \to s'$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B)
(A) edge node[left]{$f$} (A')
(C) edge node[right]{$g$} (C')
(A') edge node[below] {$i'$} (D)
(C') edge node[below] {$o'$} (D)
(B) edge node [left] {$h$} (D);
\end{tikzpicture}
\]
to this map of structured cospans:
\[
\begin{tikzpicture}[scale=1.5,baseline=(current bounding box.center)]
\node (A) at (0,0.5) {$(a,I_a)$};
\node (A') at (0,-0.5) {$(a',I_{a'}$};
\node (B) at (1.5,0.5) {$(m,s)$};
\node (C) at (3,0.5) {$(b,I_b)$};
\node (C') at (3,-0.5) {$(b',I_{b'}$.};
\node (D) at (1.5,-0.5) {$(m',s')$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$(i,!)$} (B)
(C) edge node[above]{$(o,!)$} (B)
(A) edge node[left]{$L(f)$} (A')
(C) edge node[right]{$L(g)$} (C')
(A') edge node[below] {$(i',!)$} (D)
(C') edge node[below] {$(o',!)$} (D)
(B) edge node [left] {$(h,\tau)$} (D);
\end{tikzpicture}
\]

@@

\node (L) at (1,-1.5) {$\tau_{1_b} = 1_{I_b}$};
